\documentclass[10pt]{article}

\usepackage[top=1.25in,bottom=1.25in,left=1.25in,right=1.25in]{geometry}
\usepackage{crush}

\usepackage{enumitem}

\usepackage{microtype}

\hyphenpenalty=10000
\tolerance=2000
\emergencystretch=1pt

\newcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\newenvironment{packeditem}{
\vspace{-5mm}
\begin{itemize}[leftmargin=*,labelindent=8pt]
  \renewcommand{\labelitemi}{$\diamond$}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\newcommand{\category}[2]{
\begin{center}
\vskip 6pt
\begin{tabular*}{\textwidth}{@{}p{0.75in}@{\quad\;\;}p{4in}@{\quad\quad}p{0.7in}}
%\begin{tabular*}{\textwidth}{@{}p{1in}p{4.8in}}
\vcrush[t]{1in}{\textsc{#1}} &
#2
\end{tabular*}
\end{center}
}

\newcommand{\categoryB}[2]{
\begin{center}
\vskip 6pt
\begin{tabular*}{\textwidth}{@{}p{0.75in}@{\quad\;\;}p{4.4in}@{\quad\quad}p{0.3in}}
%\begin{tabular*}{\textwidth}{@{}p{1in}p{4.8in}}
\vcrush[t]{1in}{\textsc{#1}} &
#2
\end{tabular*}
\end{center}
}


\newcommand{\n}{\\ & }
\newcommand{\nn}{\\ \n}
%\newcommand{\DT}[1]{\hspace{\stretch 1} \textit{#1}}
\newcommand{\DT}[1]{&\hspace{\stretch 1}\textit{#1}}
\newcommand{\conf}[1]{&\hspace{\stretch 1}\crushr{\textit{#1}}}
\newcommand{\citem}{~$\diamond$~}

\newcommand{\ed}[1]{}
\newcommand{\present}{\phantom{2012}}

\usepackage{url}
\urlstyle{sf}

\usepackage[nonormalsize,mathlf]{MinionPro}
\usepackage[scaled=0.75]{beramono}

\begin{document}

% ------ Header --------------------------------------------------------

{\LARGE \bf \sc
\noindent Phillip Lopes Mates\hspace{\stretch 1}
Resume
}
\vskip 10pt
\hrule

% ------ Address --------------------------------------------------------

\begin{center}
\vskip -5pt
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}

\begin{tabular}[t]{ll}
% Northeastern, CCIS\\
% 308 West Village H \\
% 360 Huntington Avenue \\
{\small\bf Resides:} & {\small Berlin, Germany} \\
{\small\bf Citizenship:} & {\small USA, Brazil}

\end{tabular} &

\begin{tabular}[t]{ll}
{\small\bf Email:} & {\small \url{phillip.mates@pm.me}}\\
{\small\bf Web:} & {\small \url{https://philomates.org}}\\
% {\small\bf Phone:} & {\small +1 801 518 3298} \\
\end{tabular}

\end{tabular*}
\end{center}

\vskip -6pt
\hrule

% --------- Statement ---------------------------------------------------

\category{Statement}{
I'm an engineer interested in building well-measured software, is discerning about tooling, and places precedence on the development process. I’m happiest when building products that empower users and facilitate social change.
}

% -------- Work experience --------------------------------------------

\category{Experience}{
{\bf Software Engineer}, Nextjournal, Berlin, DE\conf{2022 -- Jul. 2024}\n
Part of a small team using Clojure/script and Datomic to solve supply-chain problems. We employ modable-development, strive to keep our toolset small and honed, and are learning to navigate the balances between simplicity and completeness.\n\n

{\bf Compilers Engineer}, Igalia, Remote\conf{Aug. -- Dec. 2021}\n
Implemented the Shadow Realms JavaScript feature in JavaScriptCore and explored an unboxing optimization in the V8 JavaScript engine.\n\n

{\bf Data Infrastructure Engineer}, Nubank, Berlin, DE\conf{2017 -- 2021}\n
\begin{packeditem}
\item \emph{Data infrastructure:} Innovating over our ETL for Datomic-backed services and developing data processing tools used by hundreds of internal clients.
\item \emph{Testing frameworks:} Maintainer of several key testing tools at Nubank.
\item \emph{Technical lead:} Set technical priorities for a small team focused on data ingestion and publishing.
\end{packeditem}\n

{\bf Software Engineer}, Nubank, S\~{a}o Paulo, BR \conf{Feb. -- Oct. 2017}\n
\begin{packeditem}
\item \emph{Microservices:} Build and maintain microservices in Clojure for a mobile-driven credit card product
\item \emph{Engineering productivity:} Build tools and improve core Clojure libraries to boost the eﬃciency of a 100+ engineering team.
\end{packeditem}\n

{\bf Software Engineer}, Dimagi, Boston, MA \conf{2015 -- 2017}\n
\begin{packeditem}
\item \emph{CommCare:} improved stability and performance of an Android app used by tens of thousands of users world-wide. Implemented new features for users with low tech literacy.
\item \emph{Tests:} established unit-level Robolectric and UI-level Calabash test systems for Android. Built an integration test-suite between mobile and server apps. Setup cross-repository CI system.
\item \emph{Legacy code:} performed substantial refactors on a 5-year-old production legacy codebase. Migrated from Java 3 to 8 and from the Ant to Gradle build system.
\item \emph{User empathy:} Worked with users to make development in the CommCare app building platform more approachable and efficient.
\end{packeditem}

% {\bf Research Student}, Northeastern University, Boston, MA \conf{2012 -- 2014}\n
% Used type systems to prove correctness and security properties about compilers. Realized proofs using both paper/pencil and assisted methods.
% \nn

% {\bf Software Engineer Intern}, Google, Santa Monica, CA \conf{Summer 2011}\n
% Built a domain name classifier to enforce policy violations and developed
% internal analytics scripts.\nn
}

% -------- Publications --------------------------------------------

\categoryB{Publications}
{
{\bf Under Control: Compositionally Correct Closure Conversion with Mutable State} \conf{\mbox{PPDP 2019}}\n
P. Mates, J. Perconti and A. Ahmed\n
{\em Principles and Practice of Declarative Programming}\nn

{\bf A Provenance-Based Infrastructure to Support the Life Cycle of Executable Papers} \conf{\mbox{ICCS 2011}}\n
D. Koop, E. Santos, P. Mates, H. Vo, P. Bonnet, B. Bauer, B. Surer, M. Troyer, D. Williams, J. Tohline, J. Freire and C. Silva.\n
{\em International Conference on Computational Science}\nn

{\bf CrowdLabs: Social Analysis and Visualization for the Sciences} \conf{\mbox{SSDBM 2011}}\n
P. Mates, E. Santos, J. Freire and C. Silva\n
{\em International Conference on Scientific and Statistical Database Management}\nn

{\bf The ALPS project release 2.0:}\n
{\bf Open source software for strongly correlated systems} \conf{\mbox{JSTAT 2011}}\n
B. Bauer et al. (ALPS collaboration).\n
{\em Journal of Statistical Mechanics: Theory and Experiment}\nn

{\bf Towards Supporting Collaborative Data Analysis and Visualization}\n
{\bf in a Coastal Margin Observatory} \conf{\mbox{CSCW 2010}}\n
E. Santos, P. Mates, E. Anderson, B. Grimm, J. Freire and C. Silva\n
{\em Workshop on The Changing Dynamics of Scientific Collaboration}\nn
}
\vspace{-3em}
% -------- Talks --------------------------------------------
\category{Talks}{
{\bf The rise and fall of e2e at scale} \DT{April 2019}\n
Dutch Clojure Days, Amsterdam, NL\nn
{\bf How we test at Nubank} \DT{April 2018}\n
Dutch Clojure Days, Amsterdam, NL\nn
{\bf  Kripke Logical Relation for Affine Functions:}\n
{\bf The Story of a Free Theorem in the Presence of Non-termination} \DT{Sept. 2013}\n
The 2nd ACM SIGPLAN Workshop on Higher-Order Programming with Effects, Boston, MA\nn
}
\vspace{-3em}
% ------- Education ---------------------------------------------------

\category{Education}{
  {\bf Northeastern University}, Boston, MA \DT{\ed{September }2012 -- \ed{December }2014}\n
  MS in Computer Science, Programming Languages focus\n
  \n
{\bf University of Utah}, Salt Lake City, UT \DT{\ed{August }2008 -- \ed{December }2011}\n
BS with honors in Computer Science, \emph{December 2011}
}

% -------- Technical Skills --------------------------------------------

\category{Technical Skills}{
  {\bf Languages:} Clojure, Java, Scala, Python, Racket \n
  {\bf Platforms/Tools:} Datomic, Kafka, Android
}

% -------- Posters --------------------------------------------
% \category{Posters}{
% {\bf Analyzing Android Applications with Abstract Interpretation} \DT{ICFP 2012}\n
% Student Research Competition}
% \vspace{-1em}
% -------- Teaching --------------------------------------------
% \category{Teaching \mbox{experience}}{
% {\bf Teaching assistant}, CS2500 \textit{Introduction to Programming and Computing} \DT{2012,2014}\n
% Introductory undergraduate CS course at Northeastern University modeled off of ``How to Design Programs''.}

% \category{References}{
% \citem
% Amal Ahmed, amal@ccs.neu.edu \conf{Assistant Professor} \n
% \quad College of Computer and Information Science at NEU \n
% \citem
% Matt Might, might@cs.utah.edu \conf{Associate Professor} \n
% \quad School of Computing at U of U \n
% \citem
% Claudio T. Silva, csilva@nyu.edu \conf{Professor} \n
% \quad Computer Science and Engineering at NYU Poly
% }


\end{document}
