\documentclass[10pt]{article}

\usepackage[top=1.25in,bottom=1.25in,left=1.25in,right=1.25in]{geometry}
\usepackage{crush}

\usepackage{microtype}

\hyphenpenalty=10000
\tolerance=2000
\emergencystretch=1pt

\newcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

\newcommand{\category}[2]{
\begin{center}
\vskip 6pt
\begin{tabular*}{\textwidth}{@{}p{0.75in}@{\quad\;\;}p{4in}@{\quad\quad}p{0.7in}}
%\begin{tabular*}{\textwidth}{@{}p{1in}p{4.8in}}
\vcrush[t]{1in}{\textsc{#1}} &
#2
\end{tabular*}
\end{center}
}

\newcommand{\categoryB}[2]{
\begin{center}
\vskip 6pt
\begin{tabular*}{\textwidth}{@{}p{0.75in}@{\quad\;\;}p{4.4in}@{\quad\quad}p{0.3in}}
%\begin{tabular*}{\textwidth}{@{}p{1in}p{4.8in}}
\vcrush[t]{1in}{\textsc{#1}} &
#2
\end{tabular*}
\end{center}
}


\newcommand{\n}{\\ & }
\newcommand{\nn}{\\ \n}
%\newcommand{\DT}[1]{\hspace{\stretch 1} \textit{#1}}
\newcommand{\DT}[1]{&\hspace{\stretch 1}\textit{#1}}
\newcommand{\conf}[1]{&\hspace{\stretch 1}\crushr{\textit{#1}}}
\newcommand{\citem}{~$\diamond$~}

\newcommand{\ed}[1]{}
\newcommand{\present}{\phantom{2012}}

\usepackage{url}
\urlstyle{sf}

%\usepackage[T1]{fontenc}
%\usepackage[bitstream-charter]{mathdesign}

%% \usepackage[T1]{fontenc}
%%\usepackage{kpfonts}

%\usepackage{tgtermes}

\usepackage[nonormalsize,mathlf]{MinionPro}
%\usepackage[medfamily,sansmath,scale=0.88]{MyriadPro}
\usepackage[scaled=0.75]{beramono}

%\usepackage[adobe-utopia]{mathdesign}

%\usepackage{tgpagella}
%\usepackage{mathpazo}

%\usepackage{mathptmx}

%\ed{
%% \usepackage{fontspec} 
%% \usepackage{xunicode}
%% \usepackage{xltxtra}
%% \defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
%% \setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Hoefler Text}
%% %\setromanfont{Linux Libertine O}
%% \setmonofont[Scale=0.8]{Monaco} 
%% \setsansfont[Scale=0.9]{Optima Regular} 
% ---- CUSTOM AMPERSAND
%\newcommand{\amper}{{\fontspec[Scale=.95]{Hoefler Text}\selectfont\itshape\&}}
%}

%% \setromanfont [Ligatures={Common}, BoldFont={Gentium Basic Bold}, ItalicFont={Gentium Basic Italic}]{Gentium Basic}
%% \setmonofont[Scale=0.8]{Monaco} 

\begin{document}

%\thispagestyle{empty}

% ------ Header --------------------------------------------------------

{\LARGE \bf \sc
\noindent Phillip Mates\hspace{\stretch 1}
Curriculum Vitae
}
\vskip 10pt
\hrule

% ------ Address --------------------------------------------------------

\begin{center}
\vskip -5pt
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}

\begin{tabular}[t]{l}
Northeastern, CCIS\\
308 West Village H \\
360 Huntington Avenue \\
Boston, MA 02115\\

\end{tabular} &

\begin{tabular}[t]{ll}
{\small\bf Email:} & {\small \url{mates@ccs.neu.edu}}\\
{\small\bf Web:} & {\small \url{http://www.ccs.neu.edu/home/mates/}}\\
{\small\bf Phone:} & {\small +1 801 518 3298} \\
{\small\bf Citizenship:} & {\small USA, Brazil}
\end{tabular}

\end{tabular*}
\end{center}

\vskip -6pt
\hrule

% --------- Research ----------------------------------------------------

\category{Research \mbox{interests}}{
Compiler verification, type systems, and static analysis}

% ------- Education ---------------------------------------------------

\category{Education}{
{\bf Northeastern University}, Boston, MA \DT{\ed{September }2012 -- \ed{current }}\n
PhD in Computer Science, \emph{ongoing}\n
\begin{tabular}{@{}p{0.65in}@{\;\;}l@{}}
  Advisor:&Amal Ahmed\\
\end{tabular}\nn

{\bf University of Utah}, Salt Lake City, UT \DT{\ed{August }2008 -- \ed{December }2011}\n
BS with honors in Computer Science, \emph{December 2011} \n
}

% ------- Internships  ---------------------------------------------------

\category{\mbox{Internships~\textit{\&}} Training}{

{\bf PhD summer schools} \n
\citem Oregon Programming Languages Summer School \DT{\ed{July }2012} \n
\citem Institut Henri Poincar\'e thematic trimester: \n
\quad Semantics of proofs and certified mathematics \DT{\ed{August }2014}%
}

% -------- Publications --------------------------------------------

\categoryB{Publications}
{

{\bf A Provenance-Based Infrastructure to Support the Life Cycle of Executable Papers} \conf{\mbox{ICCS 2011}}\n
D. Koop, E. Santos, P. Mates, H. Vo, P. Bonnet, B. Bauer, B. Surer, M. Troyer, D. Williams, J. Tohline, J. Freire and C. Silva.\n
{\em International Conference on Computational Science}\nn

{\bf CrowdLabs: Social Analysis and Visualization for the Sciences} \conf{\mbox{SSDBM 2011}}\n
P. Mates, E. Santos, J. Freire and C. Silva\n
{\em International Conference on Scientific and Statistical Database Management}\nn

{\bf The ALPS project release 2.0:}\n
{\bf Open source software for strongly correlated systems} \conf{\mbox{JSTAT 2011}}\n
B. Bauer et al. (ALPS collaboration).\n
{\em Journal of Statistical Mechanics: Theory and Experiment}\nn

{\bf Towards Supporting Collaborative Data Analysis and Visualization}\n
{\bf in a Coastal Margin Observatory} \conf{\mbox{CSCW 2010}}\n
E. Santos, P. Mates, E. Anderson, B. Grimm, J. Freire and C. Silva\n
{\em Workshop on The Changing Dynamics of Scientific Collaboration}\nn
}

% -------- Work experience --------------------------------------------

\category{Programming \mbox{~\textit{\&} Research} \mbox{experience}}{

{\bf Research Assistant}, University of Utah, UT \conf{Summer 2012}\n
Built a static analyzer capable of statically verifying permission usage of Android applications.
The analyzer targeted Dalvik byte-code and supported higher-order control flow.\n
Mentor: Matthew Might\nn

{\bf Software Engineer}, Space Monkey, UT \conf{Summer 2012}\n
Developed device monitoring software in Node.js during a brief period between my undergraduate and graduate studies.\nn

{\bf Software Engineer Intern}, Google Santa Monica, CA \conf{2011}\n
Built a domain name classifier to enforce policy violations and developed
internal analytics scripts.\n
Mentor: Joe Vanderwaart\nn

{\bf Visiting Research Student}, Institute for Theoretical Physics, ETH Z\"urich \DT{2010}\n
Worked with Computational Physicists to create useful data management
tools.  Surveyed the field of Randomness Extractors and explored possible
implementation designs for use in Monte Carlo simulations.\n
Mentor: Matthias Troyer\nn

{\bf Research Undergrad}, Scientific Computing and Imaging Institute, UT \conf{2009 -- 2010}\n
Lead developer of an online visualization repository which leveraged the
VisTrails system to foster collaboration and enable scientists to easily
present and share their visualizations.  Developer for the VisTrails
open-source provenance and workflow management system.\n
Mentor: Claudio Silva\nn

}


% -------- Talks --------------------------------------------

\category{Talks}{

{\bf  Kripke Logical Relation for Affine Functions:}\n
{\bf The Story of a Free Theorem in the Presence of Non-termination} \DT{Sept. 2013}\n
The 2nd ACM SIGPLAN Workshop on Higher-Order Programming with Effects, Boston, MA\nn
}

% -------- Posters --------------------------------------------

\category{Posters}{
{\bf Analyzing Android Applications with Abstract Interpretation} \DT{ICFP 2012}\n
Student Research Competition
}


% -------- Teaching --------------------------------------------

\category{Teaching \mbox{experience}}{
{\bf Teaching assistant}, CS2500 \textit{Introduction to Programming and Computing} \DT{2012,2014}\n
Introductory undergraduate CS course at Northeastern University modeled off of ``How to Design Programs''.
}
% -------- Technical Skills --------------------------------------------

\category{Technical Skills}{
  {\bf Proficient:} Python \n
  {\bf Familiar:} Coq, Haskell, Racket, plus the usual suite of OO languages \n
}

\category{References}{
  Upon request.
}

\end{document}
